A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Gave molecular bond example for labelled edges

Maximum common subgraph problems come in many variants. For example, often
vertices have labels (for example, denoting what kind of atom they represent in
a molecule), and vertices may only be mapped to like-labelled vertices. We now
outline how to adapt \cref{McSplitAlg} to handle this and other cases.

>>>>

Maximum common subgraph problems come in many variants. For example, often
vertices or edges have labels (for example, denoting what kind of atom or bond they represent in
a molecule), and vertices may only be mapped to like-labelled vertices. We now
outline how to adapt \cref{McSplitAlg} to handle this and other cases.
